\bf\mftitle

### 2011-03-01 doc/jInfer/autoeditor/autoeditor.tex
autoeditor final touch in progress

\noindent \begin{tabular}{|l|l|} \hline
Responsible developer: & Mário Mikula \\ \hline
Required tokens:       & org.openide.windows.WindowManager \\ \hline
Provided tokens:       & none \\ \hline
Module dependencies:   & Base \\ 
					   & JUNG \\ \hline
Public packages:       & cz.cuni.mff.ksi.jinfer.autoeditor \\ 
					   & cz.cuni.mff.ksi.jinfer.autoeditor.automatonvisualizer \\
   					   & cz.cuni.mff.ksi.jinfer.autoeditor.automatonvisualizer.layouts \\
   					   & cz.cuni.mff.ksi.jinfer.autoeditor.gui.component \\ \hline
\end{tabular}

@@

        @Override
        public String transform(final Step<Regexp<T>> step) {
          StringBuilder sb = new StringBuilder();
          sb.append("{");
          sb.append(symbolToString.toString(step.getAcceptSymbol()));
          sb.append("|");
          sb.append(String.valueOf(step.getUseCount()));
          sb.append("}");
          return sb.toString();
        }
      };

>>>>

\noindent \begin{tabular}{|l|l|} \hline
Responsible developer & Mário Mikula \\ \hline
Required tokens       & org.openide.windows.WindowManager \\ \hline
Provided tokens       & none \\ \hline
Module dependencies   & Base \\ 
					   & JUNG \\ \hline
Public packages       & \code{cz.cuni.mff.ksi.jinfer.autoeditor} \\ 
					   & \code{cz.cuni.mff.ksi.jinfer.autoeditor.automatonvisualizer} \\
   					   & \code{cz.cuni.mff.ksi.jinfer.autoeditor.automatonvisualizer.layouts} \\
   					   & \code{cz.cuni.mff.ksi.jinfer.autoeditor.gui.component} \\ \hline
\end{tabular}

@@

        @Override
        public String transform(Step<Regexp<T>> step) {
          StringBuilder sb = new StringBuilder();
          sb.append("{");
          sb.append(symbolToString.toString(step.getAcceptSymbol()));
          sb.append("|");
          sb.append(String.valueOf(step.getUseCount()));
          sb.append("}");
          return sb.toString();
        }
      };
